---
title: "TB CSAP RSLR Estimates"
author: "Ed Sherwood <esherwood@epchc.org>"
date: "August 28, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(crosstalk)
library(plotly)
knitr::opts_chunk$set(echo = TRUE)
```

## Get Data
Tampa Bay's Claimte Science Advisory Panel (TBCSAP 2015; <http://pinellas.ifas.ufl.edu/marine/documents/CSAP_SLR_Recommendation_FINAL.pdf>) have made regional recommendations for sea level rise projections to unify efforts of local scienticts, managers and planners. Relative  <http://www.corpsclimate.us/ccaceslcurves.cfm> . When using the USACE Sea Level Change Curve Calculator Tool, first select the “St. Petersburg, FL” gauge, then choose “NOAA et al. 2012” as the output agency and factor the projected SLC rate as “Regionally Corrected.”
```{r slr_prjections}
slr_wide <- read.csv("./data-raw/TB_CSAP_Regional_SLR_Recommendations.csv")

head(slr)

slr <- gather(data = slr_wide, curve, estimate, NOAA_LOW:NOAA_HIGH, factor_key = T)
#slr_plot <- SharedData$new(slr, ~curve, group = "Choose a curve")
#slr_group <- group_by(slr, curve)
```

## Make Some Interactive Plots

Make some interactive plots to depict relative sea level rise at the St. Pete NOAA tidal gauge <https://tidesandcurrents.noaa.gov/stationhome.html?id=8726520>.

```{r slr_plots, echo=FALSE}
#Generic plot of various NOAA et al. 2012 projections
noaa <- slr %>% 
        group_by(curve) %>% 
        plot_ly(x = ~Year, y = ~estimate) %>% 
        add_lines(alpha = 0.2, name = "Other Projections")

#Highlight a specific curve
noaa %>% 
  filter(curve == "NOAA_INT_HIGH") %>%
  add_lines(name = "NOAA Intermediate High") %>% 
  layout(title = "St. Petersburg, FL, ID: 8726520\nNOAA's Regional Rate: 0.00860 feet/yr",
         yaxis = list(title="Relative Sea Level Rise (ft)"),
         legend = list(x = 0.1, y = 0.9)) %>% 
  layout(paper_bgcolor='transparent') 

#Create an html widget in default plotly account 
api_create(x = last_plot(), filename = "slr_noaa_int_high", sharing = "public")

```
## Import Summary Data from Tampa Bay Blue Carbon Assessment Project
```{r get_tbbca_data}
#Get habitat extent data 
extent <- read.csv("./data-raw/TBBCA_extent_summary_data.csv")
head(extent)

#Get GHG data
ghg <- read.csv("./data-raw/TBBCA_cseq_summary_data.csv")
head(ghg)
```

## Make a Highlighted Plot of a Select Run's Habitat Extent Changes
```{r extent_plot_code}
a <- list(
  text = "Total Blue Carbon Habitats",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

b <- list(
  text = "Mangroves",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

c <- list(
  text = "Salt Marshes",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

d <- list(
  text = "Salt Barrens",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

e <- list(
  text = "Seagrass",
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = 1,
  showarrow = FALSE
)

var = "Run 1"

tot_plot <- extent %>%
        group_by(group) %>% 
        filter(habitat=="Total Blue Carbon Habitats") %>% 
        plot_ly(x = ~year, y = ~extent) %>% 
        add_lines(line =list(dash = "dash", color = "#1f77b4"), 
                  alpha = 0.2, name = "Other Runs", showlegend = FALSE)

tot <- tot_plot %>%
        filter(group == var) %>% 
        add_lines(line=list(color="#ff7f0e"), name = var, showlegend = TRUE) %>%
        layout(annotations = a) %>% 
        layout(yaxis = list(title = "")) %>% 
        layout(paper_bgcolor='transparent') %>% 
        layout(legend = list(x = 0.01, y = 0.98))

man_plot <- extent %>%
        group_by(group) %>% 
        filter(habitat=="Mangroves") %>% 
        plot_ly(x = ~year, y = ~extent) %>% 
        add_lines(line =list(dash = "dash", color = "#1f77b4"), 
                  alpha = 0.2, name = "Other Runs", showlegend = FALSE)

man <- man_plot %>%
        filter(group == var) %>% 
        add_lines(line=list(color="#ff7f0e"), name = var, showlegend = FALSE) %>%
        layout(annotations = b) %>% 
        layout(yaxis = list(title = "")) %>% 
        layout(paper_bgcolor='transparent') 

sm_plot <- extent %>%
        group_by(group) %>% 
        filter(habitat=="Salt Marsh") %>% 
        plot_ly(x = ~year, y = ~extent) %>% 
        add_lines(line =list(dash = "dash", color = "#1f77b4"), 
                  alpha = 0.2, name = "Other Runs", showlegend = FALSE)

sm <- sm_plot %>%
        filter(group == var) %>% 
        add_lines(line=list(color="#ff7f0e"), name = var, showlegend = FALSE) %>%
        layout(annotations = c) %>% 
        layout(yaxis = list(title = "Extent(hectares)")) %>% 
        layout(paper_bgcolor='transparent') 

sb_plot <- extent %>%
        group_by(group) %>% 
        filter(habitat=="Salt Barrens") %>% 
        plot_ly(x = ~year, y = ~extent) %>% 
        add_lines(line =list(dash = "dash", color = "#1f77b4"), 
                  alpha = 0.2, name = "Other Runs", showlegend = FALSE)

sb <- sb_plot %>%
        filter(group == var) %>% 
        add_lines(line=list(color="#ff7f0e"), name = var, showlegend = FALSE) %>%
        layout(annotations = d) %>%
        layout(yaxis = list(title = "")) %>% 
        layout(paper_bgcolor='transparent') 

sg_plot <- extent %>%
        group_by(group) %>% 
        filter(habitat=="Seagrass") %>% 
        plot_ly(x = ~year, y = ~extent) %>% 
        add_lines(line =list(dash = "dash", color = "#1f77b4"),
                  alpha = 0.2, name = "Other Runs", showlegend = FALSE)

sg <- sg_plot %>%
        filter(group == var) %>% 
        add_lines(line=list(color="#ff7f0e"), name = var, showlegend = FALSE) %>%
        layout(annotations = e) %>%
        layout(yaxis = list(title = "")) %>% 
        layout(paper_bgcolor='transparent') 

hab_extent <- subplot(tot, man, sm, sb, sg, 
                      nrows = 5, shareX = TRUE, titleY = TRUE, titleX = FALSE)
hab_extent                             
api_create(x = hab_extent, filename = "run6_hab_extent", sharing = "public")
```

## Plot net CO2 sequestered estimates for select Runs
```{r net_co2_plot_code}
var = "Run 6"
ghg2 <- ghg %>%
            filter(group %in% c("Baseline", "Runs 1-6")) %>%
            group_by(habitat)
ghg3 <- ghg %>%
            filter(group %in% c("Baseline", var)) %>%
            group_by(habitat)

error_plot <- plot_ly(data=ghg2[which(ghg2$habitat == 'Total Blue Carbon Habitats'),],
                      x = ~year, y = ~net_seq, 
                      error_y = list(type = "ghg2", array = ~error), 
                      type = "scatter", mode = "lines+markers",
                      name = "Total Blue Carbon Habitats") %>% 
             add_trace(data = ghg2[which(ghg2$habitat == 'Mangroves'),],
                       name = 'Mangroves') %>%
             add_trace(data = ghg2[which(ghg2$habitat == 'Seagrass'),],
                       name = 'Seagrass') %>%
             add_trace(data = ghg2[which(ghg2$habitat == 'Salt Marsh'),],
                       name = 'Salt Marsh') %>% 
             add_trace(data = ghg2[which(ghg2$habitat == 'Salt Barrens'),],
                       name = 'Salt Barrens') %>%
             add_trace(data=ghg3, name = var,
                      x = ~year, y = ~net_seq, color = I("black"), alpha = 0.3,
                      line =list(dash = "dash")) %>% 
             layout(yaxis = list(title="Projected Net Green House Gas Sequestered<br>by Habitat (tonnes CO<sup>2</sup> eq. &plusmn; 1 S.D.)")) %>%
             layout(xaxis = list(title = "")) %>% 
             layout(paper_bgcolor='transparent') %>% 
             layout(legend = list(x = 0.01, y = 1))

api_create(x = error_plot, filename = "run6_netco2", sharing = "public")
```


